---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/repurrrsive)](https://CRAN.R-project.org/package=repurrrsive)
[![R-CMD-check](https://github.com/jennybc/repurrrsive/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jennybc/repurrrsive/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/jennybc/repurrrsive/branch/main/graph/badge.svg)](https://app.codecov.io/gh/jennybc/repurrrsive?branch=main)
<!-- badges: end -->

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", error = TRUE,
                      fig.path = "README-")
library(repurrrsive)
```

# repurrrsive

The repurrrsive package provides recursive lists that are handy when teaching or exampling functions such as `purrr::map()` and the [rectangling functions](https://tidyr.tidyverse.org/articles/rectangle.html) in the tidyr package.
The datasets are stored as R list, JSON, and XML to provide the full non-rectangular data experience.
Enjoy!

This package also includes the main data frame from the [gapminder package](https://CRAN.R-project.org/package=gapminder) in 3 different forms: simple data frame (no list-columns), data frame nested by country, and split into a named list of data frames.

## Installation

You can install repurrrsive from CRAN like so:

```{r cran-installation, eval = FALSE}
install.packages("repurrrsive")
```

or from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jennybc/repurrrsive")
```

## Recursive list examples

repurrrsive contains several datasets that are recursive lists, both in the form of R objects and as JSON and/or XML files.

For example, `got_chars` is a list with information on the `r length(got_chars)` point-of-view characters from the first five books in the Song of Ice and Fire series by George R. R. Martin.
Here's how to use `purrr::map_chr()` to extract the character's names:

```{r}
library(repurrrsive)
library(purrr)

map_chr(got_chars, "name")
```

Each set of recursive lists has its own article that gives a sense of what sort of manipulations can be demonstrated with the dataset(s):

* Game of Thrones characters
* Data on entities in the Star Wars universe
* GitHub user and repo data
* Sharla Gelfand's music collection
* Color palettes from Wes Anderson movies

Learn more at <https://jennybc.github.io/repurrrsive/articles/>.

## Nested and split data frames

The Gapminder data, from the [gapminder package](https://github.com/jennybc/gapminder), is also here in various forms to allow practice of different styles of grouped computation.

For example, the `gap_nested` dataset has one row per country, with a nested `data` column containing longitudinal data for life expectancy, population, and GDP per capita.

```{r}
gap_nested
```
