---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# repurrrsive

The repurrrsive package provides recursive lists that are handy when teaching or exampling functions such as `purrr::map()`.

Will eventually be used in this tutorial:

<https://jennybc.github.io/purrr-tutorial/>

## Installation

You can install repurrrsive from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jennybc/repurrrsive")
```

## Usage

`wesanderson` is a recursive list of color palettes, from the [wesanderson package](https://cran.r-project.org/package=wesanderson).

```{r lists}
devtools::load_all()
library(purrr)
wesanderson[1:3]
map_chr(wesanderson, 1)
map_chr(wesanderson[7:9], paste, collapse = ", ")
```

Practice bringing data from JSON into an R list.

```{r json}
library(jsonlite)
json <- fromJSON(wesanderson_json())
json$wesanderson[1:3]
identical(wesanderson, json$wesanderson)
```

Practice bringing data into R from XML. You can get it into an R list with `xml2::as_list()`, but to get a list as nice as those above? That requires a bit more work. Such is XML life.

```{r xml}
library(xml2)
xml <- xml2::read_xml(wesanderson_xml())
xml_child(xml)
as_list(xml_child(xml))
```

