---
title: "Game of Thrones data"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(repurrrsive)
```

`got_chars` is a list with information on the `r length(got_chars)` point-of-view characters from the first five books in the Song of Ice and Fire series by George R. R. Martin.
The data was retrieved from [An API Of Ice And Fire](https://anapioficeandfire.com).

```{r}
library(purrr)
(nms <- map_chr(got_chars, "name"))
map_dfr(got_chars, `[`, c("name", "gender", "culture", "born"))
```

The same `got_chars` data is also present as JSON and XML files.
Accessor functions provide the local file path.

```{r}
got_chars_json()
got_chars_xml()
```

You can practice bringing data from JSON into an R list.

```{r}
library(jsonlite)
json <- fromJSON(got_chars_json(), simplifyDataFrame = FALSE)
json[[1]][c("name", "titles", "playedBy")]
identical(got_chars, json)
```

You can practice bringing data into R from XML.
You can get it into an R list with `xml2::as_list()`, but to get a list as nice as those above? That requires a bit more work.
Such is XML life.

```{r}
library(xml2)
xml <- read_xml(got_chars_xml())
xml_child(xml)
```
