---
title: "GitHub user and repo data"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(repurrrsive)
```

`gh_users` and `gh_repos` are lists with information for 6 GitHub users and up to 30 of each user's repositories.

```{r}
library(purrr)

map_chr(gh_users, "login")
map_chr(gh_users, 18)
map_dfr(gh_users, `[`, c("login", "name", "id", "location"))
```

Peek at some info from first repo for the first user.

```{r}
str(gh_repos[[1]][[1]][c("full_name", "html_url", "description")])
```

Get full name of each user's 11th repo.

```{r}
map_chr(gh_repos, list(11, "full_name"))
```

Do you want to parse it yourself?
There are functions that return the paths to local JSON and XML files.

```{r}
c(gh_users_json(), gh_repos_json(), gh_users_xml(), gh_repos_xml())
```

Let's get the full name of each user's 11th repo, but this time using the XML representation.

```{r}
library(xml2)

repo_xml <- read_xml(gh_repos_xml())
repo_names <- map_chr(xml_find_all(repo_xml, "//full_name"), xml_text)
elevenses <- 
  11 + cumsum(c(0, head(table(gsub("(.*)/.*", "\\1", repo_names)), -1)))
repo_names[elevenses]
```
