---
title: "Star Wars data"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(repurrrsive)
```

`sw_people`, `sw_films`, `sw_species`, `sw_planets`, `sw_starships` and `sw_vehicles` are interrelated lists about entities in the Star Wars Universe.
The data was originally retrieved from the Star Wars API previously available at `http://swapi.co` using the R package [rwars](https://github.com/Ironholds/rwars).
The Star Wars API appears to have moved to `https://pipedream.com/apps/swapi` since that time.

```{r}
library(purrr)
map_chr(sw_films, "title") 
```

Elements that contain URLs provide a way to link the lists together.
For example, the `films` element of each person contains URLs for the films they have appeared in.
For example, Luke Skywalker has been in five films.

```{r}
luke <- sw_people[[1]]
names(luke)
luke[["films"]]
```

These URLs can be looked up in the the `sw_films` list to find the titles of the films.

```{r}
# Create a mapping between titles and urls
film_lookup <- map_chr(sw_films, "title") %>% 
  set_names(map_chr(sw_films, "url"))

# The films Luke is in
film_lookup[luke[["films"]]] %>% unname()
```
